Evaluating Variable Importances

### 2019-07-11 Scripts/evaluating_variable_importances.Rmd
added 5kb

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
annots <- gsub(paste(c("Gm12878-", 
                             "-Haib.bed", 
                             "-Sydh.bed",
                             "-Uta.bed",
                             "-Uw.bed",
                             "-Broad.bed",
                             "-Uchicago.bed"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]
```

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562")
annots <- gsub(paste(c("K562-", 
                             "-Haib.bed", 
                             "-Sydh.bed",
                             "-Uta.bed",
                             "-Uw.bed",
                             "-Broad.bed",
                             "-Uchicago.bed"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]
```

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
annots <- annots[grep("Gm12878", annots)]
annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
annots <- annots[grep("K562", annots)]
annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
annots <- annots[grep("Gm12878", annots)]
annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
annots <- annots[grep("K562", annots)]
annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)

>>>>

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/TFBS")
annots <- gsub(paste(c("Gm12878-", 
                             "-Haib.bed", 
                             "-Sydh.bed",
                             "-Uta.bed",
                             "-Uw.bed",
                             "-Broad.bed",
                             "-Uchicago.bed"), collapse = "|"), "", annots)
```

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/TFBS")
annots <- gsub(paste(c("K562-", 
                             "-Haib.bed", 
                             "-Sydh.bed",
                             "-Uta.bed",
                             "-Uw.bed",
                             "-Broad.bed",
                             "-Uchicago.bed"), collapse = "|"), "", annots)
```

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/BroadHMM")
annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/BroadHMM")
annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/HistoneModifications")
annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/HistoneModifications")
annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)
